The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-06-29 paper.tex
Created new folder for reports.

%\documentclass[aps,rmp,twocolumn,amsmath,amssymb,nofootinbib,superscripta
%ddress]{revtex4}
\documentclass[times,final]{elsarticle}
\usepackage{revip}
\usepackage{framed,multirow}
\usepackage{hyperref,mathrsfs,amsmath,amssymb,latexsym}

\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\op}[2]{\hat{\textbf{#1}}_{#2}}
\newcommand{\dagop}[2]{\hat{\textbf{#1}}_{#2}^\dag}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

Linear optics play a prominent role in quantum information processing. Photons make fantastic ``flying" qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}. In 2001, Knill, Laflamme and Milburn (KLM) showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting \cite{bib:KLM01}. Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure. Combined with the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.

@@

Another approach to linear optics is to pack more features known as degrees of freedom onto a single photon, and to increase the degree of control over them. It is possible to manipulate degrees of freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM, new proposals for linear optical quantum computations (LOQC) have surfaced \cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}. Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, and secure quantum computations \cite{bib:Tan16} that might be hard or impossible with a classical system.  Such methods open up new ways to engineer quantum states and quantum operations, and expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy.

@@

If the linear optical transformations can be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}. This approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.

@@

%\begin{figure}[!htb]
%\centering
%\includegraphics[width=0.3\columnwidth]{cluster_state}
%\caption{The representation of cluster states as a graph. Vertices
% represent qubits initialised into the $\ket{+}$ state, while edges 
%represent the application on {\sc cphase} gates, the ordering of which is 
%irrelevant.} \label{fig:cluster}	
%\end{figure}

@@

%\begin{figure}[!htb]
%\centering
%\includegraphics[width=0.4\columnwidth]{fusion}
%\caption{Fusion gates for joining smaller cluster states into larger ones. 
%Both require only a single polarising beamsplitter, and waveplates. The 
%type-I and -II fusion gates consume 1 or 2 qubits (photons) respectively, 
%creating an edge between the remaining graphs. The type-I gate consumes one 
%fewer photon, but requires number-resolved detection on the detected mode. 
%The type-II gate requires only on/off photodetection, but consumes an 
%additional photon. Thus, the type-I gate can be employed to fuse two Bell 
%pairs into a 3-qubit cluster state, whereas the type-II gate will only grow 
%clusters when beginning with at least 3 qubits per cluster.} %
%\label{fig:fusion}	
%\end{figure}

%\section{Linear optical networks}\label{sec:network}

%\subsection{Waveguides}

%Numerous experimental implementations of various linear optics protocols 
%have been demonstrated, using a variety of architectures. 
%The main contenders considered to date are: bulk-optics; waveguides; and 
%time-bin encoding.
%The early implementations of linear optics protocols relied on bulk-optics 
%implementations, in which a circuit is decomposed into a discrete 
%arrangement of optical components, specifically beamsplitters and phase-
%shifters. This corresponds to a direct implementation of the Reck \emph{et 
%al.~}decomposition shown in Fig.~\ref{fig:Reck}, or subsequent alternate 
%decompositions. Although this approach is effective and conceptually 
%straightforward, it is highly impractical for large interferometers. For 
%example, the implementation of a 100-mode interferometer requires on the 
%order of 10,000 discrete optical elements, which must all be simultaneously 
%aligned with interferometric stability, a highly experimentally challenging 
%problem, not to mention incredibly physically large.

%Alternately, integrated waveguide devices can be employed to implement 
%identical decompositions by etching the modes into paths in an optical 
%chip, where evanescent coupling between closely neighbouring modes 
%implements beamsplitter operations. Such devices are extremely compact, 
%allowing the miniaturisation of large numbers of optical elements. 
%Importantly, such devices are extremely optically stable, mitigating the 
%need for any kind of dynamic stabilisation

@@

\begin{figure}
\centering
\begin{subfigure}{.5\columnwidth}
  \centering
  \includegraphics[width=0.7\columnwidth]{full_architecture}
  \caption{}
  \label{fig:FL_arch}
\end{subfigure}%
\begin{subfigure}{0.5\columnwidth}
  \centering
  \includegraphics[width=0.8\columnwidth]{PBS_TB}
  \caption{}
  \label{fig:fusion}
\end{subfigure}
\caption{(a) A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train. (b) Mapping between two polarisation-encoded qubits undergoing a polarising beamsplitter (PBS) operation, and its equivalent representation using 4 time-bins in a pulse-train. The PBS completely reflects (transmits) the vertical (horizontal) polarisations. The evolution of the four logical basis states, and their respective outputs, are shown explicitly. Writing out this PBS transformation in matrix form yields a permutation. Taking this permutation and relabelling the modes, we obtain the time-bin transformation shown underneath -- a simple swap of two of the four time-bins.}
\label{fig:PBS_TB}
\end{figure}

%\begin{figure}[!htb]
%\centering
%\includegraphics[width=0.4\columnwidth]{full_architecture}
%\caption{A fibre-loop architecture for implementing arbitrary linear optics 
%operations upon a time-bin-encoded pulse-train.
%The source prepares the temporally encoded pulse-train, with time-bin 
%separation $\tau$.
%The pulse-train then enters a dual-loop configuration. The inner loop has 
%%length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is 
%the number of optical modes). The architecture is controlled via three 
%dynamically controlled beamsplitters. The first and last need only be on/
%off switches, whose sole purpose is to couple in the prepared pulse-
%train, keep it within the outer loop for the required duration, and then 
%couple out of the outer loop, yielding the transformed pulse-train. The 
%central beamsplitter must be able to implement arbitrary classically-
%controlled beamsplitter operations.
%} \label{fig:FL_arch}	
%\end{figure}

@@

PNR detectors are a wonderful addition to the toolbox of linear optics. A notable example is the superconducting transition edge sensor (TES) which has an extremely high quantum efficiency. The principle it operates on is very similar to the SNSPD, but with a much higher sensitivity that allows it to detect the energy of single photons.
%low dark count rates. However, they are quite slow, have low maximum 
%counting rates, and are costly to operate due to their very low operating 
%temperatures. 
The visible light photon counter (VLPC) is another kind of PNR detector. The way VLPC works is in principle very similar to the APD, but with an additional layer of silicon that is lightly doped with arsenic (As). Owing to the presence of the As, a single photon absorption event always create an electrical signal that is always of the same magnitude. Thus, the output electrical signal is just proportional to the number of detected photons.
Last, PNR detectors can be created by connecting many non-PNR detectors in parallel to one another, and summing the signals at the output. For instance, like in the theoretical proposal of \cite{bib:Sperling12}. Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Eraerds07,bib:Afek09,bib:Kalashnikov12,bib:Chrapkiewicz14,bib:Chen17}.

@@

The difficulty in producing nonlinear operations required for universal LOQC led researchers to seek out alternative ways for demonstrating its power in the near term. {\sc Bosonsampling} is the result of such an effort. It is a restricted model of non-universal quantum computation \cite{bib:Aaronson11} that constitutes sampling the photocounts from the probability distribution of identical bosons scattered by a passive linear optical interferometer. While not universal, the {\sc bosonsampling} scheme is strongly believed to implement a classically hard task. Consider such a circuit of $m$ input (and output) modes that is injected with $n$ indistinguishable single photons such that $m\sim \mathcal{O}(n^2)$. Then, the boson sampling task consists of generating a sample from the probability distribution of single-photon measurements at the output of the circuit. The probability of detecting a $s_j$ photons at the $j$th output mode is
\begin{align}
p(s_1,\ldots,s_m)=\frac{{\rm Per}(U_S)}{s_1!\ldots s_n!} \ ,	
\end{align}
where ${\rm Per}$ denotes the permanent of a matrix, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first n columns and repeating its $j$th row $s_j$ times. The appearance of the permanent, which is of \#P complexity, in this statistics contributes to the hardness of the boson sampling problem. It is also known to be as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.3\columnwidth]{BS_model}
\caption{The Boson-Sampling model. A string of n single
photons is prepared in m optical modes. They are evolved
via a passive interferometer $U$. Finally the photon-statistics
are sampled from the distribution $p(s_1,\ldots,s_m)$.
} \label{fig:FL_arch}	
\end{figure}

 Owing to the simplicity of {\sc BosonSampling} and its overarching implications for computer science, multiple experiments were reported shortly after its theoretical conception \cite{bib:Tillmann13,bib:Spring13, bib:Broome13,bib:Crespi13}. A recent experiment showed a {\sc bosonsampling} machine beating an early computer \cite{bib:WangHe16}.
{\sc BosonSampling} has piqued so much interest, that a complete discussion would make up its own review, so we shall only outline some main developments here. One variant, known as scattershot {\sc bosonsampling}, proposes using pumped SPDC heralded photon sources to increase the rate of generating input photons \cite{bib:Lund14,bib:Bentivegna15}. Others varied the source input to cat-states \cite{bib:Rohde15} and thermal states \cite{bib:Tamma14_thermal} . An exciting modification allows the determination of molecular vibronic spectra \cite{bib:Huh15}, a task that goes beyond demonstrating a computationally hard task.

@@

As experimental imperfections threaten the scalability of {\sc bosonsampling}, there have been efforts to look into its error tolerance \cite{bib:Rohde12_tol}, fault-tolerance \cite{bib:Leverrier15}, and experimental artefacts \cite{bib:Shchesnobich14,bib:Tamma16}. Some works have resulted in interesting connections to exotic mathematical entities like immanants \cite{bib:Tan2013,bib:deGuise2014} and the multi-dimensional permanent \cite{bib:Tichy15}. A time-bin implementation of {\sc bosonsampling} \cite{bib:Motes14} seems particularly attractive in terms of robustness \cite{bib:Motes15}.

@@

 As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling is readily available, but executes a task that is believed to be hard classically. Surprisingly, an entanglement between a large number of path labels is possible with single photons in a passive linear optical device. Motes {\it et al.~} harnessed this so-called number-path entanglement for quantum metrology without the use of entangled states \cite{bib:Motes15}. Here, the phase shift to be estimated, $\varphi$, manifests itself as a linear phase gradient across $N$ modes (See Fig. \ref{fig:MORDOR}). By straddling these modes among a quantum Fourier transform and its conjugate operation, it is possible to achieve $\Delta \varphi=\mathcal{O}(N^{-3/2})$ using a coincidence measurement with just a string of $N$ single photons, for up to at least $N=25$ modes.

 Quantum multi-parameter estimation is the extension of quantum phase estimation to sense multiple phases in a multi-arm inetrferometer \cite{bib:Szczykulska16}. Theoretical work has shown that it is favorable to probe all phases simultaneously rather than individually \cite{bib:Baumgratz16,bib:Ciampini16}, and it remains to realize existing proposals for implememtation \cite{bib:Spagnolo12}. Nonetheless, for a Heisenberg-limited sensitivity, entangled states and joint measurements across modes are likely to be required.

 %\begin{figure}[!htb]
%\centering
%\includegraphics[width=0.4\columnwidth]{MORDOR}
%\caption{Architecture of the quantum Fourier transform interferometer for 
%metrology using single-photon states. QFT: Quantum Fourier transform 
%circuit, and $\varphi_k=(k-1)\varphi$. Single photons are injected into the 
%input modes on the left-hand-side, and a $N$-fold coincidence measurement 
%is conducted at the output on the right-hand-side.} \label{fig:MORDOR}	
%\end{figure}

\begin{figure}
\centering
\begin{subfigure}{.5\columnwidth}
  \centering
  \includegraphics[width=0.5\columnwidth]{phE}
  \caption{}
   \label{fig:MZ}
\end{subfigure}%
\begin{subfigure}{0.5\columnwidth}
  \centering
  \includegraphics[width=0.8\columnwidth]{MORDOR}
  \caption{}
  \label{fig:fusion}
\end{subfigure}
\caption{(a) A schematic diagram of the Mach-Zehnder interferometer comprising of two 50/50 beamsplitters with a phase shift $\varphi$ in one of its two paths.	(b) Architecture of the quantum Fourier transform interferometer for metrology using single-photon states. QFT: Quantum Fourier transform circuit, and $\varphi_k=(k-1)\varphi$. Single photons are injected into the input modes on the left-hand-side, and a $N$-fold coincidence measurement is conducted at the output on the right-hand-side.}
\label{fig:MORDOR}
\end{figure}

@@

Linear optics interferometry has become a leading contender for the implementation of quantum information processing protocols. The preparation, manipulation and measurement of photonic quantum information has become mainstream and widely employed, with impressive experimental accuracies.

We have discussed the various ways in which quantum information can be represented photonically, how they can be manipulated and detected, and some of their leading applications.

>>>>

%\documentclass[aps,rmp,twocolumn,amsmath,amssymb,nofootinbib,superscripta
%ddress]{revtex4}

\documentclass[times,final]{elsarticle}
\usepackage{revip}
\usepackage{framed,multirow}
\usepackage{hyperref,mathrsfs,amsmath,amssymb,latexsym}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\op}[2]{\hat{\textbf{#1}}_{#2}}
\newcommand{\dagop}[2]{\hat{\textbf{#1}}_{#2}^\dag}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

Linear optics play a prominent role in quantum information processing. Photons make fantastic `flying' qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}. In 2001, Knill, Laflamme and Milburn (KLM) showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting \cite{bib:KLM01}. Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure. Combined with the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.

@@

Another approach to linear optics is to pack more features known as degrees of freedom onto a single photon, and to increase the degree of control over them. It is possible to manipulate degrees of freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM, new proposals for linear optical quantum computations (LOQC) have surfaced \cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}. \sihui {Some of them support new functionalities like secure delegated quantum computations \cite{bib:Barz12,bib:Fisher14}}. Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}}, and secure quantum computations \cite{bib:Tan16} that might be hard or impossible with a classical system.  Such methods open up new ways to engineer quantum states and quantum operations, and expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy.

@@

If the linear optical transformations \sihui{is to} be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}. This approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.

@@

@@

@@

\begin{figure}
\centering
\begin{subfigure}{.5\columnwidth}
  \centering
  \includegraphics[width=0.7\columnwidth]{full_architecture}
  \caption{}
  \label{fig:FL_arch}
\end{subfigure}%
\begin{subfigure}{0.5\columnwidth}
  \centering
  \includegraphics[width=0.8\columnwidth]{PBS_TB}
  \caption{}
  \label{fig:PBS_TB}
\end{subfigure}
\caption{(a) A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train. (b) Mapping between two polarisation-encoded qubits undergoing a polarising beamsplitter (PBS) operation, and its equivalent representation using 4 time-bins in a pulse-train. The PBS completely reflects (transmits) the vertical (horizontal) polarisations. The evolution of the four logical basis states, and their respective outputs, are shown explicitly. Writing out this PBS transformation in matrix form yields a permutation. Taking this permutation and relabelling the modes, we obtain the time-bin transformation shown underneath -- a simple swap of two of the four time-bins.}
\end{figure}

@@

PNR detectors are a wonderful addition to the \sihui{linear optical} toolbox. A notable example is the superconducting transition edge sensor (TES) which has an extremely high quantum efficiency. The principle it operates on is very similar to the SNSPD, but with a much higher sensitivity that allows it to detect the energy of single photons.
%low dark count rates. However, they are quite slow, have low maximum 
%counting rates, and are costly to operate due to their very low operating 
%temperatures. 
The visible light photon counter (VLPC) is another kind of PNR detector. The way VLPC works is in principle very similar to the APD, but with an additional layer of silicon that is lightly doped with arsenic (As). Owing to the presence of the As, a single photon absorption event always create an electrical signal that is always of the same magnitude. Thus, the output electrical signal is just proportional to the number of detected photons.
Last, PNR detectors can be created by connecting many non-PNR detectors in parallel to one another, and summing the signals at the output. For instance, like in the theoretical proposal of \cite{bib:Sperling12}. Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Kalashnikov12,bib:Chrapkiewicz14,bib:Heilmanndc15}.

@@

The difficulty in producing nonlinear operations required for universal LOQC led researchers to seek out alternative ways for demonstrating its power in the near term. {\sc Bosonsampling} is the result of such an effort. It is a restricted model of non-universal quantum computation \cite{bib:Aaronson11} that constitutes sampling the photocounts from the probability distribution of identical bosons scattered by a passive linear optical interferometer. While not universal, the {\sc bosonsampling} scheme is strongly believed to implement a classically hard task. Consider such a circuit of $m$ input (and output) modes that is injected with $n$ indistinguishable single photons such that $m\sim \mathcal{O}(n^2)$. Then, the boson-sampling task consists of generating a sample from the probability distribution of single-photon measurements at the output of the circuit. The probability of detecting $s_j$ photons at the $j$th output mode is
\begin{align}
p(s_1,\ldots,s_m)=\frac{|{\rm Per}(U_S)|^2}{s_1!\ldots s_n!} \ ,	
\end{align}
where ${\rm Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first $n$ columns and repeating its $j$th row $s_j$ times. The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard), in this statistics contributes to the hardness of the boson-sampling problem. Note that the number of configurations $|S|=\binom{n+m-1}{n}$ in the output superposition scales exponentially with $m$. For this reason, the boson sampler does not let us \emph{calculate} matrix permanents, as this would require knowing individual amplitudes with high precision, which would require an exponential number of samples. Rather, the boson sampler samples across a distribution of permanents without actually revealing any of them to the experimenter. Nonetheless, this is a classically intractable problem. It is also known that boson-sampling is as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.3\columnwidth]{BS_model}
\caption{The Boson-Sampling model. A string of n single
photons is prepared in m optical modes. They are evolved
via a passive interferometer $U$. Finally the photon-statistics
are sampled from the distribution $p(s_1,\ldots,s_m)$.
} \label{fig:BosonSampling}	
\end{figure}

 Owing to the simplicity of {\sc BosonSampling} and its overarching implications for computer science, multiple experiments were reported shortly after its theoretical conception \cite{bib:Tillmann13,bib:Spring13, bib:Broome13,bib:Crespi13}. A recent experiment showed a {\sc bosonsampling} machine beating an early computer \cite{bib:WangHe16}.
{\sc BosonSampling} has piqued so much interest, that a complete discussion would make up its own review, so we shall only outline some main developments here. One variant, known as scattershot {\sc bosonsampling}, proposes using pumped SPDC heralded photon sources to increase the rate of generating input photons \cite{bib:Lund14,bib:Bentivegna15}, by inputting an SPDC source into \emph{every} mode rather than just the first $n$, thereby boosting the probability of preparing the desired $n$ photons. Others varied the source input to cat-states \cite{bib:Rohde15} and thermal states \cite{bib:Tamma14_thermal} . An exciting modification allows the determination of molecular vibronic spectra \cite{bib:Huh15}, a task that goes beyond demonstrating a computationally hard task.

@@

As experimental imperfections threaten the scalability of {\sc bosonsampling}, there have been efforts to look into its error tolerance \cite{bib:Rohde12_tol}, fault-tolerance \cite{bib:Leverrier15}, and experimental artefacts \cite{bib:Shchesnobich14,bib:Tamma16}. Some works have resulted in interesting connections to exotic mathematical entities like immanants \cite{bib:Tan2013,bib:deGuise2014} and the multi-dimensional permanent \cite{bib:Tichy15}. A time-bin implementation of {\sc bosonsampling} \cite{bib:Motes14} seems particularly attractive in terms of robustness \cite{bib:Motes15_timebin}.

@@

 As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling is readily available, but executes a task that is believed to be hard classically. Surprisingly, an entanglement between a large number of path labels is possible with single photons in a passive linear optical device. Motes {\it et al.~}harnessed this so-called number-path entanglement for quantum metrology without the use of entangled states \cite{bib:Motes15_LOQM}. Here, the phase shift to be estimated, $\varphi$, manifests itself as a linear phase gradient across $N$ modes (See Fig. \ref{fig:MORDOR}). By straddling these modes among a quantum Fourier transform and its conjugate operation, it is possible to achieve $\Delta \varphi=\mathcal{O}(N^{-3/2})$ using a coincidence measurement with just a string of $N$ single photons, for up to at least $N=25$ modes.

 Quantum multi-parameter estimation is the extension of quantum phase estimation to sense multiple phases in a multi-arm interferometer \cite{bib:Szczykulska16}. Theoretical work has shown that it is favorable to probe all phases simultaneously rather than individually \cite{bib:Baumgratz16,bib:Ciampini16}, and it remains to realize existing proposals for implementation \cite{bib:Spagnolo12}. Nonetheless, for a Heisenberg-limited sensitivity, entangled states and joint measurements across modes are likely to be required.

\begin{figure}
\centering
\begin{subfigure}{.5\columnwidth}
  \centering
  \includegraphics[width=0.5\columnwidth]{phE}
  \caption{}
   \label{fig:MZ}
\end{subfigure}%
\begin{subfigure}{0.5\columnwidth}
  \centering
  \includegraphics[width=0.8\columnwidth]{MORDOR}
  \caption{}
  \label{fig:MORDOR}
\end{subfigure}
\caption{(a) A schematic diagram of the Mach-Zehnder interferometer comprising of two 50/50 beamsplitters with a phase shift $\varphi$ in one of its two paths.	(b) Architecture of the quantum Fourier transform interferometer for metrology using single-photon states. QFT: Quantum Fourier transform circuit, and $\varphi_k=(k-1)\varphi$. Single photons are injected into the input modes on the left-hand-side, and a $N$-fold coincidence measurement is conducted at the output on the right-hand-side.}
\end{figure}

@@

Linear optical interferometry has become a leading contender for the implementation of quantum information processing protocols. The preparation, manipulation and measurement of photonic quantum information has become mainstream and widely employed, with impressive experimental accuracies.

We have discussed the various ways in which quantum information can be represented \sihui{in photonics}, how they can be manipulated and detected, and some of their leading applications.

### 2017-06-29 submitted/paper.tex
Created new folder for reports.

Another approach to linear optics is to pack more features known as degrees of freedom onto a single photon, and to increase the degree of control over them. It is possible to manipulate degrees of freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM, new proposals for linear optical quantum computations (LOQC) have surfaced \cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}. \sihui {Some of them support new functionalities like secure delegated quantum computations \cite{bib:Barz12,bib:Fisher14}}. Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}}, and secure quantum computations \cite{bib:Tan16} that might be hard or impossible with a classical system.  Such methods open up new ways to engineer quantum states and quantum operations, and expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy.

@@

If the linear optical transformations \sihui{is to} be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}. This approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.

@@

PNR detectors are a wonderful addition to the \sihui{linear optical} toolbox. A notable example is the superconducting transition edge sensor (TES) which has an extremely high quantum efficiency. The principle it operates on is very similar to the SNSPD, but with a much higher sensitivity that allows it to detect the energy of single photons.
%low dark count rates. However, they are quite slow, have low maximum 
%counting rates, and are costly to operate due to their very low operating 
%temperatures. 
The visible light photon counter (VLPC) is another kind of PNR detector. The way VLPC works is in principle very similar to the APD, but with an additional layer of silicon that is lightly doped with arsenic (As). Owing to the presence of the As, a single photon absorption event always create an electrical signal that is always of the same magnitude. Thus, the output electrical signal is just proportional to the number of detected photons.
Last, PNR detectors can be created by connecting many non-PNR detectors in parallel to one another, and summing the signals at the output. For instance, like in the theoretical proposal of \cite{bib:Sperling12}. Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Kalashnikov12,bib:Chrapkiewicz14,bib:Heilmanndc15}.

@@

We have discussed the various ways in which quantum information can be represented \sihui{in photonics}, how they can be manipulated and detected, and some of their leading applications.

>>>>

Another approach to linear optics is to pack more features known as degrees of freedom onto a single photon, and to increase the degree of control over them. It is possible to manipulate degrees of freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM, new proposals for linear optical quantum computations (LOQC) have surfaced \cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}. Some of them support new functionalities like secure delegated quantum computations \cite{bib:Barz12,bib:Fisher14}. Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, encrypted quantum walks \cite{bib:Rohde_qw12}, and secure quantum computations \cite{bib:Tan16} that might be hard or impossible with a classical system.  Such methods open up new ways to engineer quantum states and quantum operations, and expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy.

@@

If the linear optical transformations is to be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}. This approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.

@@

PNR detectors are a wonderful addition to the linear optical toolbox. A notable example is the superconducting transition edge sensor (TES) which has an extremely high quantum efficiency. The principle it operates on is very similar to the SNSPD, but with a much higher sensitivity that allows it to detect the energy of single photons.
%low dark count rates. However, they are quite slow, have low maximum 
%counting rates, and are costly to operate due to their very low operating 
%temperatures. 
The visible light photon counter (VLPC) is another kind of PNR detector. The way VLPC works is in principle very similar to the APD, but with an additional layer of silicon that is lightly doped with arsenic (As). Owing to the presence of the As, a single photon absorption event always create an electrical signal that is always of the same magnitude. Thus, the output electrical signal is just proportional to the number of detected photons.
Last, PNR detectors can be created by connecting many non-PNR detectors in parallel to one another, and summing the signals at the output. For instance, like in the theoretical proposal of \cite{bib:Sperling12}. Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Kalashnikov12,bib:Chrapkiewicz14,bib:Heilmanndc15}.

@@

We have discussed the various ways in which quantum information can be represented in photonics, how they can be manipulated and detected, and some of their leading applications.
